Experiences with Planning for Natural Language Generation

### 2008-06-23 trunk/Papers/experiences/experiments.tex
changes to experiments (GIVE subsection)

Results for the $h=20$, $n=5$ case (with $w$ ranging from $1$ to $70$) are
shown in Figure~\ref{fig:give-runtime-junk}. As in Experiment~2, FF again
runs out of memory, this time at $w=17$. SGPLAN happily solves inputs
beyond $w=70$. However, unlike in Experiment 2, both planners now spend a
substantial propertion of their time on grounding. In SGPLAN, this
translates to a ``parsing time'' (which \todo{presumably} includes
grounding) which grows from 180 ms to 21.7 seconds as $w$ grows from $1$ to
$75$. The rest of the runtime (which also includes the search time) only
grows from 400 ms to 2.3 seconds. This difference is particularly dramatic
given that the actual optimal plan in each case is an identical plan of
about 100 steps. The overall runtimes in these instances is also concerning
since runtimes over a couple seconds negatively affect the response time of
the GIVE system.

>>>>

Results for the $h=20$, $n=5$ case (with $w$ ranging from $1$ to $70$) are
shown in Figure~\ref{fig:give-runtime-junk}. As in Experiment~2, FF again
runs out of memory, this time at $w=17$. SGPLAN happily solves inputs
beyond $w=70$. However, unlike in Experiment 2, both planners now spend a
substantial propertion of their time on grounding. In SGPLAN, this
translates to a ``parsing time'' (which \todo{presumably} includes
grounding) which grows from 180 ms to 21.7 seconds as $w$ grows from $1$ to
$75$. The rest of the runtime (which also includes the search time) only
grows from 400 ms to 2.3 seconds. This difference is particularly dramatic
given that the actual optimal plan in each case is an identical plan of
about 100 steps. The planning times for these instances are also concerning
since times over a couple seconds negatively affect the overall response
time of the system, which must react in real time to user actions.
